### 2022-01-17 newvariant.tex
done

For example, if we assume epidemic strength $\RR$ is known, then variation in the generation-interval distribution has no effects on the estimated effectiveness of a constant-strength intervention.
In this same case, however, assuming longer generation intervals results in a slower estimated epidemic growth rate (lower $r$), making an epidemic look easier to control with a constant-speed intervention.
Conversely, when epidemic speed $r$ is fixed, assuming longer generation intervals leads to a higher estimate of epidemic strength ($\RR$), making the epidemic look harder to control with a constant-strength intervention.
Constant-strength and -speed interventions are idealized representations of real-life interventions, which can vary from strength-like (e.g., vaccination and social distancing) or speed-like (e.g., contact tracing and isolation) depending on how their effectiveness varies across the generation interval (see \cite{doi:10.1098/rspb.2020.1556} and Discussion).

>>>>

For example, if we assume epidemic strength $\RR$ is known, then variation in the generation-interval distribution has no effects on the estimated effectiveness of a constant-strength intervention.
In this same case, however, assuming longer generation intervals results in a slower estimated epidemic growth rate (lower $r$), making an epidemic look easier to control with a constant-speed intervention.
Conversely, when epidemic speed $r$ is fixed, assuming longer generation intervals leads to a higher estimate of epidemic strength ($\RR$), making the epidemic look harder to control with a constant-strength intervention.
Constant-strength and -speed interventions are idealized representations of real-life interventions, which can vary from strength-like (e.g., vaccination and social distancing) to speed-like (e.g., contact tracing and isolation) depending on how their effectiveness varies across the generation interval (see \cite{doi:10.1098/rspb.2020.1556} and Discussion).
